Self-Supervised Transfer Learning From 2D Images to 3D Point Clouds

### 2022-05-02 doc/paper.tex
updates results

\begin{table*}[t!]
    \centering
    \resizebox{0.7\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c}
                                       & 5\%         & 10\% & 20\%        & 30\%        & 40\%        & 100\%       \\
            \hline
            Scratch                    & 26.9        & 31.1 & 40.7        & 42.2        & 45.7        & 49.0        \\
            \hline
            PointContrast              & 27.0 (+0.1) & 35.3 & 40.5 (-0.2) & 43.0 (+0.8) & 43.9 (-1.8) & 49.1 (+0.1) \\
            Contrastive Scene Contexts & 29.8 (+2.9) & 35.5 & 41.6 (+0.9) & 42.9 (+0.7) & 44.6 (-1.1) & 49.3 (+0.3) \\
            CME \textbf{(Ours)}        & 25.5 (-1.4) & 35.5 & 39.1 (-1.6) & 42.4 (+0.2) & 43.6 (-2.1) & 48.5 (-0.5) \\
        \end{tabular}
    }
    \caption{Scannet Instance Segmentation with Partial Data  (mAP@0.5)}
    \label{table:scannetInstanceVaryingDataAmount}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{\textwidth}{!}{
        \begin{tabular}[b]{ c | l c c c c c c c c c c c c c c c c c | c }
                                       & \begin{turn}{-90}cabinet \end{turn} & \begin{turn}{-90} bed  \end{turn} & \begin{turn}{-90} chair \end{turn} & \begin{turn}{-90} sofa \end{turn} & \begin{turn}{-90} table \end{turn} & \begin{turn}{-90} door \end{turn} & \begin{turn}{-90}  window \end{turn} & \begin{turn}{-90} bookshelf \end{turn} & \begin{turn}{-90} picture \end{turn} & \begin{turn}{-90} counter \end{turn} & \begin{turn}{-90} desk \end{turn} & \begin{turn}{-90} curtain \end{turn} & \begin{turn}{-90} refrigerator \end{turn} & \begin{turn}{-90}  Shower curtain \end{turn} & \begin{turn}{-90}  toilet \end{turn} & \begin{turn}{-90} sink  \end{turn} & \begin{turn}{-90} bathtub  \end{turn} & \begin{turn}{-90} otherfurniture \end{turn} & mAP@0.5     \\

            scratch                    & 45.8                       & 72.7                       & 79.8                       & 60.6                       & 69.5                       & 37.8                       & 28.9                       & 44.2                       & 17.8                       & 16.6                       & 24.8                       & 24.0                       & 45.3                       & 63.4                       & 93.1                       & 46.6                       & 78.5                       & 33.4                       & 49.0        \\
            \hline
            PointContrast              & 45.6                       & 68.9                       & 76.0                       & 62.7                       & 65.2                       & 38.5                       & 33.2                       & 53.7                       & 15.9                       & 20.9                       & 31.6                       & 23.2                       & 36.6                       & 55.5                       & 1.0                        & 48.0                       & 76.9                       & 31.6                       & 49.1 (+0.1) \\
            Contrastive Scene Contexts & 48.6                       & 63.5                       & 79.0                       & 64.3                       & 65.0                       & 35.9                       & 32.8                       & 48.8                       & 15.0                       & 27.1                       & 38.3                       & 19.1                       & 44.9                       & 50.4                       & 94.6                       & 49.1                       & 76.3                       & 34.3                       & 49.3 (+0.3) \\
            CME \textbf{(Ours)}        & 45.3                       & 72.8                       & 76.2                       & 66.2                       & 63.2                       & 38.2                       & 25.4                       & 49.7                       & 18.6                       & 21.0                       & 34.3                       & 20.2                       & 39.2                       & 58.9                       & 94.8                       & 45.0                       & 73.9                       & 30.0                       & 48.5 (-0.5) \\
            \hline
        \end{tabular}
    }
    \caption{Scannet Instance Segmentation Results (mAP@0.5)}
    \label{table:scannetInstanceSegmention}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{0.7\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c }
                                       & 5\%                    & 10\%                   & 20\%                   & 30\%                   & 40\%                   & 100\%                 \\
            \hline
            Scratch                    & 39.2                   & 40.43                  & 41.06                  & 41.67                  & 40.79                  & 41.01                 \\
            \hline
            PointContrast              & 40.29 \textbf{(1.09)}  & 42.59 \textbf{(+2.16)} & 42.2  \textbf{(+1.14)} & 41.65 (-0.02)          & 42.99 \textbf{(+2.2)}  &                       \\
            Contrastive Scene Contexts & 40.6 \textbf{(+1.4)}   & 42.21 \textbf{(+1.78)} & 42.26 \textbf{(+1.2)}  & 42.24 \textbf{(+0.57)} & 44.29 \textbf{(+3.5)}  & 43.01 \textbf{(+2.0)} \\
            CME \textbf{(Ours)}        & 39.49 \textbf{(+0.29)} & 40.90 \textbf{(+0.47)} & 40.91 (-0.15)          & 41.82 \textbf{(+0.15)} & 41.77 \textbf{(+0.98)} &                       \\
        \end{tabular}
    }
    \caption{KITTI Semantic Segmentation results (mIOU)}
    \label{table:kittiSemanticResults}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{0.5\textwidth}{!}{
        \begin{tabular}{c | c c c}
                                       & Scannet              & SunRGBD              \\
            \hline
            Scratch                    & 35.2                 & 32.0                 \\
            \hline
            PointContrast              & 36.7 \textbf{(+1.5)} & 34.2 \textbf{(+2.2)} \\
            Contrastive Scene Contexts & 36.1 \textbf{(+0.9)} & 35.1 \textbf{(+3.1)} \\
            CME \textbf{(Ours)}        & 37.7 \textbf{(+2.5)} & 33.1 \textbf{(+1.1)} \\
        \end{tabular}
    }
    \caption{Object Detection using VoteNet  (mAP)}
    \label{table:scannetObjectDetection}
\end{table*}

>>>>

\begin{table*}[t!]
    \centering
    \resizebox{0.7\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c}
                                       & 5\%                  & 10\%          & 20\%                 & 30\%                 & 40\%        & 100\%                \\
            \hline
            Scratch                    & 26.9                 & \textbf{31.1} & 40.7                 & 42.2                 & 45.7        & 49.0                 \\
            \hline
            PointContrast              & 27.0 \textbf{(+0.1)} & 35.3          & 40.5 (-0.2)          & 43.0 \textbf{(+0.8)} & 43.9 (-1.8) & 49.1 \textbf{(+0.1)} \\
            Contrastive Scene Contexts & 29.8 \textbf{(+2.9)} & 35.5          & 41.6 \textbf{(+0.9)} & 42.9 \textbf{(+0.7)} & 44.6 (-1.1) & 49.3 \textbf{(+0.3)} \\
            CME \textbf{(Ours)}        & 25.5 (-1.4)          & 35.5          & 39.1 (-1.6)          & 42.4 \textbf{(+0.2)} & 43.6 (-2.1) & 48.5 (-0.5)          \\
        \end{tabular}
    }
    \caption{Scannet Instance Segmentation with Partial Data  (mAP@0.5)}
    \label{table:scannetInstanceVaryingDataAmount}
\end{table*}

% \begin{table*}[t!]
%     \centering
%     \resizebox{\textwidth}{!}{
%         \begin{tabular}[b]{ c | l c c c c c c c c c c c c c c c c c | c }
%                                        & \begin{turn}{-90}cabinet \end{turn} & \begin{turn}{-90} bed  \end{turn} & \begin{turn}{-90} chair \end{turn} & \begin{turn}{-90} sofa \end{turn} & \begin{turn}{-90} table \end{turn} & \begin{turn}{-90} door \end{turn} & \begin{turn}{-90}  window \end{turn} & \begin{turn}{-90} bookshelf \end{turn} & \begin{turn}{-90} picture \end{turn} & \begin{turn}{-90} counter \end{turn} & \begin{turn}{-90} desk \end{turn} & \begin{turn}{-90} curtain \end{turn} & \begin{turn}{-90} refrigerator \end{turn} & \begin{turn}{-90}  Shower curtain \end{turn} & \begin{turn}{-90}  toilet \end{turn} & \begin{turn}{-90} sink  \end{turn} & \begin{turn}{-90} bathtub  \end{turn} & \begin{turn}{-90} otherfurniture \end{turn} & mAP@0.5     \\

%             scratch                    & 45.8                       & 72.7                       & 79.8                       & 60.6                       & 69.5                       & 37.8                       & 28.9                       & 44.2                       & 17.8                       & 16.6                       & 24.8                       & 24.0                       & 45.3                       & 63.4                       & 93.1                       & 46.6                       & 78.5                       & 33.4                       & 49.0        \\
%             \hline
%             PointContrast              & 45.6                       & 68.9                       & 76.0                       & 62.7                       & 65.2                       & 38.5                       & 33.2                       & 53.7                       & 15.9                       & 20.9                       & 31.6                       & 23.2                       & 36.6                       & 55.5                       & 1.0                        & 48.0                       & 76.9                       & 31.6                       & 49.1 (+0.1) \\
%             Contrastive Scene Contexts & 48.6                       & 63.5                       & 79.0                       & 64.3                       & 65.0                       & 35.9                       & 32.8                       & 48.8                       & 15.0                       & 27.1                       & 38.3                       & 19.1                       & 44.9                       & 50.4                       & 94.6                       & 49.1                       & 76.3                       & 34.3                       & 49.3 (+0.3) \\
%             CME \textbf{(Ours)}        & 45.3                       & 72.8                       & 76.2                       & 66.2                       & 63.2                       & 38.2                       & 25.4                       & 49.7                       & 18.6                       & 21.0                       & 34.3                       & 20.2                       & 39.2                       & 58.9                       & 94.8                       & 45.0                       & 73.9                       & 30.0                       & 48.5 (-0.5) \\
%             \hline
%         \end{tabular}
%     }
%     \caption{Scannet Instance Segmentation Results (mAP@0.5)}
%     \label{table:scannetInstanceSegmention}
% \end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{0.7\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c }
                                       & 5\%                    & 10\%                   & 20\%                   & 30\%                   & 40\%                   & 100\%                  \\
            \hline
            Scratch                    & 39.2                   & 40.43                  & 41.06                  & 41.67                  & 40.79                  & 41.01                  \\
            \hline
            PointContrast              & 40.29 \textbf{(1.09)}  & 42.59 \textbf{(+2.16)} & 42.2  \textbf{(+1.14)} & 41.65 (-0.02)          & 42.99 \textbf{(+2.2)}  & 42.09 \textbf{(+1.08)} \\
            Contrastive Scene Contexts & 40.6 \textbf{(+1.4)}   & 42.21 \textbf{(+1.78)} & 42.26 \textbf{(+1.2)}  & 42.24 \textbf{(+0.57)} & 44.29 \textbf{(+3.5)}  & 43.01 \textbf{(+2.0)}  \\
            CME \textbf{(Ours)}        & 39.49 \textbf{(+0.29)} & 40.90 \textbf{(+0.47)} & 40.91 (-0.15)          & 41.82 \textbf{(+0.15)} & 41.77 \textbf{(+0.98)} & 42.04 \textbf{(+1.03)} \\
        \end{tabular}
    }
    \caption{KITTI Semantic Segmentation results (mIOU)}
    \label{table:kittiSemanticResults}
\end{table*}

\begin{table*}[t!]
    \centering
    \resizebox{0.4\textwidth}{!}{
        \begin{tabular}{c | c c c}
                                       & Scannet              & SunRGBD              \\
            \hline
            Scratch                    & 35.2                 & 32.0                 \\
            \hline
            PointContrast              & 36.7 \textbf{(+1.5)} & 34.2 \textbf{(+2.2)} \\
            Contrastive Scene Contexts & 36.1 \textbf{(+0.9)} & 35.1 \textbf{(+3.1)} \\
            CME \textbf{(Ours)}        & 37.7 \textbf{(+2.5)} & 33.1 \textbf{(+1.1)} \\
        \end{tabular}
    }
    \caption{Object Detection using VoteNet  (mAP)}
    \label{table:scannetObjectDetection}
\end{table*}
